Project 1 FYS-STK3155

### 2022-09-08 doc/project1.tex

\Proof of $E[\hat{\beta}] = \beta$
$$E[\hat{\beta}] = E[(X^{T}X)^{-1}X^{T}y]$$
Because we are assuming $(X^{T}X)^{-1}X^{T}$ to be deterministic, $E[(X^{T}X)^{-1}X^{T}] = (X^{T}X)^{-1}X^{T}$. Moreover, we know $E[y] = y$, and we can thus rewrite the equation as follows:
$$E[(X^{T}X)^{-1}X^{T}y] = (X^{T}X)^{-1}X^{T}y = \beta$$
$\blacksquare$
\\
\\[ var[y_i] = E\left[(y_i - E[y_i])^2\right] \]

>>>>

Proof of $E[\hat{\beta}] = \beta$
$$E[\hat{\beta}] = E[(X^{T}X)^{-1}X^{T}y]$$
Because we are assuming $(X^{T}X)^{-1}X^{T}$ to be deterministic, $E[(X^{T}X)^{-1}X^{T}] = (X^{T}X)^{-1}X^{T}$. Moreover, we know $E[y] = y$, and we can thus rewrite the equation as follows:
$$E[(X^{T}X)^{-1}X^{T}y] = (X^{T}X)^{-1}X^{T}y = \beta$$
$\blacksquare$
\\
